\invisiblepart{DOSSIER : STREET SAMURAI}

\section{THE STREET SAMURAI}
\begin{multicols}{3}
\setlength{\parskip}{.05cm}

\texttt{>>>I’m not close to a lot of people. It might be my blank
silver cybereyes, or the dermal plating under my skin...or
maybe just the fact that whenever I look at someone, they
assume I have some sort of crosshair hovering over them.}

\texttt{They’re right about the crosshairs.}

\texttt{Anyway, I don’t have a lot of friends. But when the lead starts
flying, all that changes.}

\texttt{I’m chipped and wired, choombatta. I’m harder than steel,
faster than lightning, hit like an avalanche, and shoot like I
invented it. It cost me, of course. Injuries. Pain. Shitloads of
money.}

\texttt{Was it worth it? Replacing my meat with machines? The pain
of recovery, the terrible itch as it integrated, the gradual dis-
tancing of people I loved. Was it worth it, to be this good?}

\texttt{Hell yes.<<<}

\textbf{The Street Samurai} is a combat master. Often one of
toughest and most skilled combatants on the team,
the street samurai is a warrior for hire whose super-
human talents were bought with cybernetic upgrades,
relentless training, and no small amount of spilled
blood. The Street Samurai may be a hired gun, but
they take the word “samurai” very seriously, and ad-
here to a code of their own devising. On the mean
streets of the Sixth World, ther samurai is a feared—
and respected—enemy.

\subsection{CREATING A STREET SAMURAI}

\paragraph{1.  Choose your Metatype}

You may choose \textbf{Human}, \textbf{Dwarf}, \textbf{Elf}, \textbf{Ork}, or
\textbf{Troll}. Each metatype offers a selection of meta-
type moves. Choose one metatype move from
the options presented.

\paragraph{2.  Choose your look}

\textit{Glowing eyes, silvered eyes, hard eyes}

\textit{Cropped hair, wild hair, topknot}

\textit{Tattooed skin, scarred skin, camo skin}

\textit{Bulky body, lithe body, skinny body}

\paragraph{3.  Choose your name and street name}

Make up a name and street name or pick a real
name and street name from the lists and name
generators starting in the \textbf{GM Resources} section.

\paragraph{4.  Assign your stats}

You have 5 stats: Awareness, Combat, Stamina,
Craft, and Presence. Important stats for you are
Combat, Stamina, and Craft.


You have 4 \textbf{Build Points} to distribute among
your stats. To increase a stat by 1 point costs 1
Build Point. You may increase a stat to a maxi-
mum of +2 as a starting character. If you wish,
you may lower 1 stat to -1 in order to have an
additional point to spend.

\paragraph{5.  Choose your Equipment}

Choose from the lists below, or customize your
own gear using the rules in \textbf{Creating Gear} on
page 60.

\textbf{Armor:} \textit{form-fitting armor, ballistic vest, lined
coat}

\textbf{Weapon:} \textit{choose four weapons from the list
of melee and small arms}


\paragraph{6.  Choose your cyberware}

You start with the following cyberware items:


\begin{adjustwidth*}{.5cm}{.5cm}
\tcirc{} Cybereyes with low-light, thermographic,
and flare compensation capability

\tcirc{} Wired Reflexes 1 \textbf{or} Dermal Plating (+1)
\end{adjustwidth*}

These items are state of the art, fully integrated
with your biology and do not cost essence. In
addition, choose one kit from the options below
(descriptions of these items are on page 38):


\textbf{Kit 1 (5essence):} \textit{Bone lacing, skillwires,
cranial cushion}

\textbf{Kit 2 (3 essence):} \textit{cyberarm with light pistol
and smartlink}

\textbf{Kit 3 (4 essence):} \textit{Smartlink, noise filter, tacti-
cal computer, hand razors}

You can customize items using the rules in the
\textbf{Creating Cyberware} section on page 63.

\paragraph{7.  Set your Essence and Edge.}

To determine your starting Essence, subtract the
essence cost of your cyberware (if any) from 6.

You start with 4 Edge.

\paragraph{8.  Choose 2 Contacts}

Arms dealer, cybersurgeon, bartender, street
clinic nurse, private investigator, dockworker, pi-
lot, cab driver, retired runner, survival nut

\paragraph{9.  Create your Code}

The word “samurai” means something on these
streets. Create (with the help of the GM and the
other players, if you like) the code of honor that
you follow.


\paragraph{10.  Establish debts and favors}

Place one of your fellow runners’ names in at
least one of the blanks in the \textbf{Debts \& Favors}
section of your playbook. Each time a name
appears in a debt or favor, it counts as 1 Bond
with that character. The more people you have
Bond with, the better.

\paragraph{11.  Starting Funds}

You start play with 3d6 x 250¥ immediately
available.

\paragraph{12.  Starting Moves}

You know all the Core and Secondary Moves.
You also know the \textbf{Weapons Free} move and
one other Street Samurai move.

\end{multicols}

\newpage



\begin{dossier}
\dossierstatbar{THE STREET SAM}
\hspace{.5cm}%
\vrule width 2pt
\hspace{.3cm}%
\begin{dossiermovebar}
\fontsize{9pt}{1em}\selectfont
\setlength{\parskip}{.2cm}
\selectedMove{Weapons Free:} when you fire up your augmentations, roll+Combat. On 10+, you may
spend 1 Edge and activate all of your cyberware. On 7-9, it costs 2 Edge.

\unselectedMove{More Power:} when you attempt to bend, break through, or otherwise destroy some-
thing, roll+Stamina. On 10+, you easily achieve your goal. On 7-9, you break it, but (choose
1):
\begin{moveoptions}
\moveoption{ It takes longer than expected}

\moveoption{ It makes a lot of noise}

\moveoption{ You take 1 stun in the process}
\end{moveoptions}

\unselectedMove{Get Medieval:} when you deal damage to an enemy in melee, take +2 forward against
that enemy.

\unselectedMove{Shake it Off:} when you fight through the pain, roll+Stamina. On 10+, remove 2 boxes
of stun damage. On 7-9, remove 1.

\unselectedMove{Situational Awareness:} you are never surprised. If an enemy would get the drop on
you, you may act first.

\unselectedMove{State of the Art:} select one cyberware item that normally requires activation. That item
gains the always on tag.

\unselectedMove{The Only Thing Faster is Light:} whenever you Rock \& Roll, on a 12+ you may deal
your damage to a second target within range.

\unselectedMove{Pain Editor:} when you have to make a Gut Check, you are boosted. Additionally, when
you reach 9 or more wounds, you may choose to accept a chronic injury rather than bleed-
ing out. If you already have all of the chronic injuries, you cannot use this move.

\unselectedMove{Honorable:} when you uphold a tenet of your code, roll+Presence. On a 10+, hold
2. On 7-9, hold 1. You may spend this hold to pull strings, manipulate, or make someone
sweat.

\unselectedMove{Deadeye:} when you attack a surprised or defenseless enemy in ranged combat, you
can deal damage or, name your target and roll+Combat:
\begin{moveoptions}
\moveoption{ Head: on 10+, you deal your damage and they fall to the ground, stunned. 7-9: they fall
to the ground, stunned.}

\moveoption{ Arms: on 10+, you deal your damage, and they drop whatever they’re holding. 7-9: they
drop whatever they’re holding.}

\moveoption{ Legs: on 10+, you deal your damage, and they are slowed or immobilized. 7-9: they are
slowed or immobilized.}
\end{moveoptions}
\end{dossiermovebar}%
\end{dossier}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "sixth_world"
%%% End: 
