\invisiblepart{DOSSIER : FACE}

\section{THE FACE}
\begin{multicols}{3}
\setlength{\parskip}{.05cm}

\texttt{>>>I could have been on the trid - I’ve got the looks. And
half the megacorps in Seattle would kill to get me in an in-
terview. But why tie myself down like that? I have a particular
set of talents that makes me incredibly valuable in shadow-
running circles, and to be completely honest, I’m hooked on
the adrenaline.}

\texttt{It’s a rush to be someone else, to read someone’s tics and
cues, and to run a con so effective that the mark never even
figures out it happened. It’s good when it goes right. So
good.}

\texttt{On the other hand, you have to be careful who you con. You
don’t con your team. Why? I sometimes ask myself the same
thing. But then...well, lemme make a long story short. You see
this scar...?<<<}

\textbf{The Face} is the professional front of the shadowrun-
ning team. When a deal is being negotiated, the Face
is front and center. However, the Face is also a pro-
fessional con, and a master of disguise, misdirection,
and interpersonal relations. A team without the Face is
at a disadvantage in dealing with potential employers
and rivals, and with a few phone calls, the Face makes
getting into and out of any operation easier.



\subsection{CREATING A FACE}

\paragraph{1.  Choose your Metatype}

You may choose \textbf{Human}, \textbf{Dwarf}, \textbf{Elf}, \textbf{Ork}, or
\textbf{Troll}. Each metatype offers a selection of meta-
type moves. Choose one metatype move from
the options presented.

\paragraph{2.  Choose your look}

\textit{Wise eyes, jeweled eyes, laughing eyes}

\textit{Normal skin, perfect skin, synthetic skin}

\textit{Great smile, smoky stare, rugged good looks,
regal bearing}

\textit{Fit body, compact body, androgynous body}

\paragraph{3.  Choose your name and street name}

Make up a name and street name or pick a real
name and street name from the lists and name
generators starting in the \textbf{GM Resources} section.

\paragraph{4.  Assign your stats}

You have 5 stats: Awareness, Combat, Stamina,
Craft, and Presence. Important stats for you are
Awareness, Presence, and Craft.

You have 4 \textbf{Build Points} to distribute among
your stats. To increase a stat by 1 point costs 1
Build Point. You may increase a stat to a maxi-
mum of +2 as a starting character. If you wish,
you may lower 1 stat to -1 in order to have an
additional point to spend.

\paragraph{5.  Choose your Equipment}

Choose from the lists below, or customize your
own gear using the rules in \textbf{Creating Gear} on
page 60.

\textbf{Armor:} \textit{armorweave clothing, form fitting
armor, light armor jacket}

\textbf{Weapon:} \textit{Colt L36, Beretta 101T, stun baton,
taser}

\paragraph{6.  Choose your cyberware}

You may start with one of the following cyber-
ware kits (descriptions of these items are on
page 45):

\textbf{Kit 1 (2 essence):} \textit{cybereyes with thermo-
graphic vision, voice modulator}

\textbf{Kit 2 (3 essence):} \textit{FeatherTouch system, level
1 skillwires}


\paragraph{7.  Set your Essence and Edge.}

To determine your starting Essence, subtract the
essence cost of your cyberware (if any) from 6.

You start with 4 Edge.

\paragraph{8.  Choose 4 Contacts}

Club owner, Yakuza boss, car dealer, journalist,
senator’s aide, money launderer, mafia capo,
arms dealer, wealthy socialite


\paragraph{9.  Establish debts and favors}

Place one of your fellow runners’ names in at
least one of the blanks in the \textbf{Debts \& Favors}
section of your playbook. Each time a name
appears in a debt or favor, it counts as 1 Bond
with that character. The more people you have
Bond with, the better.

\paragraph{10.  Starting Funds}

You start play with 3d6 x 350¥ immediately
available.

\paragraph{11.  Starting Moves}

You know all the Core and Secondary Moves.
You also know the \textbf{Razor Insight} move, and
one other Face move.

\end{multicols}

\newpage

\begin{dossier}
\dossierstatbar{THE FACE}
\hspace{.5cm}%
\vrule width 2pt
\hspace{.3cm}%
\begin{dossiermovebar}
\fontsize{8.5pt}{1em}\selectfont
\setlength{\parskip}{.05cm}


\selectedMove{Razor Insight:} when you have a casual conversation with someone, roll+Awareness. On
10+, you learn three of the following things. On
7-9, you learn 2.
\begin{moveoptions}
\moveoption{ Something they love}

\moveoption{ Something they lost}

\moveoption{ Something they fear}

\moveoption{ Something they took}

\moveoption{ Something they need}
\end{moveoptions}
If you use this information when fast talking, manipulating, or making them sweat, you are
boosted.

\unselectedMove{Fast Talk:} when you need to convince somebody of something fast, roll+Presence. On
10+, your quick thinking gets you through. On 7-9,
they’re convinced, but (choose 1)

\begin{moveoptions}
\moveoption{ they check up on your story later}

\moveoption{ they get in serious trouble for believing
you}

\moveoption{ one of your contacts somehow ends up
involved...in a bad way}
\end{moveoptions}

\unselectedMove{Work the Angles:} when
you manipulate someone, take +1.

\unselectedMove{Come Hither:} when you attempt to seduce someone, roll+Presence. On 10+, they’re
into you, and you can get a favor from them or get access to some of their personal stuff.
On 7-9, they’re into you and will provide minor help, but it will take some more time and
TLC to get a favor from them.

\unselectedMove{Build a Legend:} when you create a false identity, spend 1 day working on it and
roll+Craft. On 10+, your legend is solid and will hold up to any scrutiny. On 7-9, it holds up
for now, but (choose 1):

\begin{moveoptions}
\moveoption{ you’ve only got 1d4+Craft days before its
blown}

\moveoption{ you run into someone who knows you...as
someone else.}

\moveoption{ you have to do something unpleasant to
maintain your cover.}
\end{moveoptions}

\unselectedMove{Crazy Smooth:} when you
Fast Talk, you are boosted.

\unselectedMove{I Know A Guy:} when you need an illegal good or service, roll+Presence. On 10+, you
know someone who can get it for you immediately, and discreetly. On 7-9, they can get it,
but (choose 1):

\begin{moveoptions}
\moveoption{ it takes 1 additional day}

\moveoption{ it costs twice as much as predicted}

\moveoption{ your fence has to drop your name to get}
it
\end{moveoptions}

\unselectedMove{Honeyed Words:} when you make someone sweat, you may roll+Presence instead of
Combat.

\unselectedMove{Chameleon:} when you attempt to blend in to a social environment, roll+Presence. On
10+, nobody questions your presence. On 7-9, you catch the eye of someone who becomes
curious about what you’re doing there.

\unselectedMove{Irresistible:} even if you anger, insult, or otherwise tick off a contact, they just can’t stay
mad at you. They only avoid you for half as long as normal.

\end{dossiermovebar}%
\end{dossier}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "sixth_world"
%%% End: 
