\invisiblepart{DOSSIER : HACKER}

\section{THE HACKER}
\begin{multicols}{3}
\setlength{\parskip}{.05cm}

\texttt{>>>These chromers and spellworms are missing the point.
They’re in this for money, looking to retire someday? Hah.
They’ve got no idea where the power is. Real power lies in
a world most of them take for granted. But it’s a world I live
and breathe. You want paydata? I know where it is. You want
me to shut some shit down? I can do that. You want me to
hack Renraku? Give me a dataline. I’ll do it. I dream in code,
babe. I can see the girl in the red dress.}

\texttt{And don’t tell anyone, but this? I do it for fun. You should see
me when I’m serious.<<<}

\textbf{The Hacker} is the master of the worldwide virtual re-
ality network of the Matrix. Able to bend the Matrix
their will, the Hacker is a critical member of the team.
From finding crucial data on targets, to locating floor-
plans of facilities, to shutting down security systems
and sabotaging response efforts, the hacker’s value is
indisputable.


\subsection{CREATING A HACKER}

\paragraph{1.  Choose your Metatype}

You may choose \textbf{Human}, \textbf{Dwarf}, \textbf{Elf}, \textbf{Ork}, or
\textbf{Troll}. Each metatype offers a selection of meta-
type moves. Choose one metatype move from
the options presented.

\paragraph{2.  Choose your look}

\textit{Cybereyes, glasses, unfocused eyes}

\textit{No hair, unkempt hair, mohawk, ponytail}

\textit{Pale skin, bad skin, tattooed skin}

\textit{Thin body, heavy body, compact body, flabby
body}

\paragraph{3.  Choose your name and street name}

Make up a name and street name or pick a real
name and street name from the lists and name
generators starting in the \textbf{GM Resources} section.

\paragraph{4.  Assign your stats}

You have 5 stats: Awareness, Combat, Stamina,
Craft, and Presence. Important stats for you are
Awareness, Craft, and Combat.

You have 4 \textbf{Build Points} to distribute among
your stats. To increase a stat by 1 point costs 1
Build Point. You may increase a stat to a maxi-
mum of +2 as a starting character. If you wish,
you may lower 1 stat to -1 in order to have an
additional point to spend.

\paragraph{5.  Choose your Equipment}

Choose from the lists below, or customize your
own gear using the rules in \textbf{Creating Gear} on
page 60.

\textbf{Armor:} \textit{trenchcoat, light armor jacket}

\textbf{Weapon:} \textit{Fichetti Needler, Ares Lightfire 70,
Combat Axe, Remington 990}

\paragraph{6.  Build your deck}

Choose one of the cyberdecks below, or con-
struct your cyberdeck using the \textbf{Creating Cyber-
decks} rules located on page 62.

\textbf{Cyberdeck:} \textit{Fuchi Cyber-4, Fuchi Cyber-7}

\paragraph{7.  Write your Programs}

Choose 3 programs from the list on page 38,
or using the rules in \textbf{Writing Programs} (page
66), create the software you wish to run on
your deck. You have 8 points to spend purchas-
ing routines for your programs. Each routine you
purchase costs 1 point.



\paragraph{8.  Choose your cyberware}

You may start with one of the following cyber-
ware kits (descriptions of these items are on
page 45):

\textbf{Kit 1 (3 essence):} \textit{cybereyes with low-light,
synaptic hardening, datajack}

\textbf{Kit 2 (2 essence):} \textit{headware cyberdeck, data-
jack}


\paragraph{9.  Set your Essence and Edge.}

To determine your starting Essence, subtract the
essence cost of your cyberware (if any) from 6.

You start with 3 Edge.

\paragraph{10.  Choose 2 Contacts}

GhostSyndicate, electronics dealer, military
hacker, gang member, former professor, ma-
trix guru, white hat, script kiddie, poker dealer,
money launderer

\paragraph{11.  Establish debts and favors}

Place one of your fellow runners’ names in at
least one of the blanks in the \textbf{Debts \& Favors}
section of your playbook. Each time a name
appears in a debt or favor, it counts as 1 Bond
with that character. The more people you have
Bond with, the better.

\paragraph{12.  Starting Funds}

You start play with 3d6 x 150¥ immediately
available.

\paragraph{13.  Starting Moves}

You know all the Core and Secondary Moves.
You also know the \textbf{Born Digital} and \textbf{Sling
Code} moves.

\end{multicols}

\newpage

\begin{dossier}
\dossierstatbar{THE HACKER}
\hspace{.5cm}%
\vrule width 2pt
\hspace{.3cm}%
\begin{dossiermovebar}
\fontsize{9pt}{1em}\selectfont
\setlength{\parskip}{.1cm}

\selectedMove{Born Digital:} while in
the Matrix, when you:
\begin{moveoptions}
\moveoption{ Stay Frosty, add your deck’s Mask rating
to the roll}

\moveoption{ Take damage, subtract your deck’s
Hardening rating from the damage}

\moveoption{ Rock \& Roll, roll+Craft instead of
+Combat}

\moveoption{ Deal damage, add your deck’s CPU to the
damage.}
\end{moveoptions}

\selectedMove{Sling Code:} when you hack a Matrix node or device, roll+Craft. On 10+, choose 3. On
7-9, choose 2:
\begin{moveoptions}
\moveoption{ The node or device is unaware of the
intrusion}

\moveoption{ You leave no trace of your presence}

\moveoption{ You don’t trigger IC}

\moveoption{ You learn a useful detail about another
node connected to this one}
\end{moveoptions}

Once in control of a node, you can issue commands
appropriate to it.

\unselectedMove{Overwatch:} when you defend a device or node against a matrix attack, roll+Aware-
ness. On 10+, the attack is ineffective. On 7-9, halve the damage or duration of the attack’s
effect.

\unselectedMove{IC Killer:} when you
inflict damage to IC, inflict +1 damage.

\unselectedMove{Interference:} when you use a device or device node you have hacked to interfere with
the enemy, Hold 1 to grant to a teammate when they
Rock \& Roll or Stay Frosty.

\unselectedMove{Deathmatch:} when you deal damage to enemy hackers, add your Combat stat to the
damage.

\unselectedMove{Multitasker:} you can
hack multiple systems or devices
simultaneously. Roll+Awareness. On 10+, you suffer no penalties to hack two systems. On 7-9, take -1 ongoing to the second
system.

\unselectedMove{Compile Agent:} you can integrate up to 6 storage worth of programs currently in
your cyberdeck’s storage into an independent matrix entity called a Agent. Only one Agent
can be active at a time. Agents have the following
characteristics:
\begin{moveoptions}
\moveoption{ CPU: allocate at least 1 point from your
cyberdeck’s CPU to the Agent’s CPU}

\moveoption{ Wounds: a Agent’s wounds are equal to its
size in storage units}

\moveoption{ Moves: Agents use the Sling Code and Born
Digital moves, substituting CPU for Craft.}

\moveoption{ Other Stats: any other stats a Agent depend on its constituent programs (e.g., if a con-
stituent program has the Armor routine, the Agent
has Armor 1)}
\end{moveoptions}

\unselectedMove{Tracer:} when you would deal damage to an enemy hacker in Matrix combat, you can
instead forgo damage to plant a tracer tag on their avatar. This tracer is active for 1+Craft
days.

\unselectedMove{Subversion:} when you would defeat an intrusion countermeasure, instead of destroying it you can subvert it’s programming and send it at an enemy. Roll+Craft. On 10+, it will
attack the enemy twice before crashing. On 7-9, it will attack once.

\end{dossiermovebar}%
\end{dossier}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "sixth_world"
%%% End: 
