\invisiblepart{DOSSIER : ADEPT}

\section{THE ADEPT}
\begin{multicols}{3}
\setlength{\parskip}{.05cm}

\texttt{>>>When the gift awakened in me, I looked inward. I stud-
ied myself. I saw my limitations - and overcame them. I rec-
ognized my flaws - and accepted them. I reached inward un-
til I held the very heart of my own power, and when I found
it, I switched it on.}

\texttt{Fast, deadly, balanced, I’m an island of focus in the mael-
strom of combat. Some people cannot grasp my true ca-
pabilities. Others don’t understand why I directed your gifts
inward, instead of outward in flashy displays. But
I know why.}

\texttt{Because in the end, when the machine fails, and the magic
dies, I will still have peace.<<<}

\textbf{The Adept} is a magic-user whose power is focused
inward, unlocking their full physical potential. Realized
in the form of performance, speed, and endurance at
or exceeding the peak of human capability, mastery
of martial combat, and total control of self, the adept’s
inner calm and perfected body are the envy of
many.

\subsection{CREATING AN ADEPT}

\paragraph{1.  Choose your Metatype}

You may choose \textbf{Human}, \textbf{Dwarf}, \textbf{Elf}, \textbf{Ork}, or
\textbf{Troll}. Each metatype offers a selection of meta-
type moves. Choose one metatype move from
the options presented.

\paragraph{2.  Choose your look}

\textit{Wise eyes, wary eyes, glowing eyes}

\textit{No hair, cropped hair, long braid}

\textit{Clean skin, tattooed skin, hard skin}

\textit{Perfect body, heavy body, lithe body}

\paragraph{3.  Choose your name and street name}

Make up a name and street name or pick a real
name and street name from the lists and name
generators starting in the \textbf{GM Resources} section.

\paragraph{4.  Assign your stats}

You have 5 stats: Awareness, Combat, Stamina,
Craft, and Presence. Important stats for you are
Awareness, Craft, and Presence.

You have 4 \textbf{Build Points} to distribute among
your stats. To increase a stat by 1 point costs 1
Build Point. You may increase a stat to a maxi-
mum of +2 as a starting character. If you wish,
you may lower 1 stat to -1 in order to have an
additional point to spend.

\paragraph{5.  Choose your Equipment}

Choose from the lists below, or customize your
own gear using the rules in \textbf{Creating Gear} on
page 60.

\textbf{Armor:} \textit{leather armor, Arcana armor}

\textbf{Weapons:} \textit{paired Ares Predators, katana, bo
staff, paired combat knives, compound bow}

\paragraph{6.  Set your Essence and Edge.}

You start with 6 Essence and 3 Edge.

\paragraph{7.  Choose 2 Contacts}

Temple master, gunsmith, underground fight
club organizer, tea shop owner, yakuza soldier,
fetishmonger

\paragraph{8.  Establish debts and favors}

Place one of your fellow runners’ names in at
least one of the blanks in the \textbf{Debts \& Favors}
section of your playbook. Each time a name
appears in a debt or favor, it counts as 1 Bond
with that character. The more people you have
Bond with, the better.

\paragraph{9.  Starting Funds}

You start play with 3d6 x 250¥ immediately
available.

\paragraph{10.  Starting Moves}

You know all the Core and Secondary Moves.
You also know the \textbf{Mystic Body} move, and
one other Adept move.

\end{multicols}

\newpage

\begin{dossier}
\dossierstatbar{THE ADEPT}
\hspace{.5cm}%
\vrule width 2pt
\hspace{.3cm}%
\begin{dossiermovebar}
\fontsize{9pt}{1em}\selectfont
\setlength{\parskip}{.2cm}
\selectedMove{Mystic Body:} when taking damage
from magical effects, your body counts as natural
mystic armor rated at your Essence divided by
three (rounded down). This move makes you eligible
to take additional Adept moves, though you may not
take more than your Essence stat. If your essence
is reduced, you may lose one or more Adept moves.

\unselectedMove{Enhanced Ability:} when you concentrate on enhancing your abilities, spend 1 Edge 
and roll+the stat you wish to enhance. On 10+, increase that stat by 1 point until the end of 
the current scene or encounter. On a 7-9, increase any stat by 1, but reduce another stat by 1 
for the equivalent time period. 

\unselectedMove{Killing Hands:} when you deal damage while unarmed, spend 1 Edge to deal lethal 
  damage instead of stun. 

  \unselectedMove{Danger Sense:} when you open your mind to the world of subtle mundane and magical 
    information in your environment, spend 1 Edge and roll+Awareness. On 10+, you cannot 
    be surprised. On 7-9, take +1 to Stay Frosty. 

    \unselectedMove{Submission Hold:} when you would deal damage to an enemy in melee, you may 
      instead forgo damage and subdue your opponent. If the opponent would normally be dangerous to touch (such as a fire elemental), you may spend 1 Edge to negate that danger. 

      \unselectedMove{Perfect Control:} when you wish to control your emotions, reactions, and nonverbal 
        cues, roll+Presence. On 10+, you can
        demonstrate any emotion or reaction you
        wish, indistinguishable from a genuine
        response. On 7-9, you maintain control,
        but (choose 1): 
\begin{moveoptions}
        \moveoption{ it is exhausting; take 1 stun }

        \moveoption{ your control will only last for a
        short time }

        \moveoption{ your effort is detectable by magical means }
\end{moveoptions}

        \unselectedMove{The Sight:} when you take time to study an enemy, roll+Awareness. On 10+, take +1 
          forward or take +2 damage forward to your next melee attack. On 7-9, take +1 forward. 

          \unselectedMove{Astral Projection:} when you project your spirit into astral space, spend 1 Edge and 
            roll+Craft. On 10+, you project successfully. On 7-9, you project, but your connection is ten- 
            uous; take -1 ongoing while in astral space. While in astral space, roll+Craft for all actions. 

            \unselectedMove{Iron Skin:} when you take damage, you may spend Edge 1-for-1 to reduce the dam- 
              age. 

              \unselectedMove{Unbreakable Defense:} when you Rock \& Roll, take +1 armor forward. 

                

\end{dossiermovebar}%
\end{dossier}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "sixth_world"
%%% End: 
