\invisiblepart{DOSSIER : COVERT OPS}

\section{THE COVERT OPS SPECIALIST}
\begin{multicols}{3}
\setlength{\parskip}{.05cm}

\texttt{>>> They call us ``ghosts''. I walk the streets feeling the eyes
  look over me and then instantly forgetting
  me. Unnoticeable. But that's fine. I prefer it
  that way, really. }

\texttt{Smash and grab runs are for amateurs. Not
my style. The people who hire me don't want
flash. They want discretion. Intellegence, theft,
or even occasional wetwork - it doesn't matter to
me. I'm in it for two things: the nuyen and the rush.}

\texttt{When you walk into a building and walk out
again with no one the wiser, that's when you're
truly a ghost. <<<}

\textbf{The Covert Ops Specialist} has perfected
the art of silent entry. Locked doors, security
systems, armed patrols -  these mean nothing to a
skilled Covert Ops Specialist. More than just a
professional thief, these individuals provide
critical support to a team trying to be
subtle. And when its time to take the gloves off,
the Covert Ops Specialist is no stranger to a
surgical assassination.


\subsection{CREATING A COVERT OPS SPECIALIST}

\paragraph{1.  Choose your Metatype}

You may choose \textbf{Human}, \textbf{Dwarf}, \textbf{Elf}, \textbf{Ork}, or
\textbf{Troll}. Each metatype offers a selection of meta-
type moves. Choose one metatype move from
the options presented.

\paragraph{2.  Choose your look}

\textit{Quick eyes, clear eyes, sharp eyes}

\textit{Short hair, ponytail, crew cut, no hair}

\textit{Body suit, street clothes, nice suit}

\textit{Long body, thin body, athletic body}

\paragraph{3.  Choose your name and street name}

Make up a name and street name or pick a real
name and street name from the lists and name
generators starting in the \textbf{GM Resources} section.

\paragraph{4.  Assign your stats}

You have 5 stats: Awareness, Combat, Stamina,
Craft, and Presence. Important stats for you are
Combat, Awareness, and Craft.


You have 4 \textbf{Build Points} to distribute among
your stats. To increase a stat by 1 point costs 1
Build Point. You may increase a stat to a maxi-
mum of +2 as a starting character. If you wish,
you may lower 1 stat to -1 in order to have an
additional point to spend.

\paragraph{5.  Choose your Equipment}

Choose from the lists below, or customize your
own gear using the rules in \textbf{Creating Gear} on
page 60.

\textbf{Armor:} \textit{chameleon suit, form-fitting armor}

\textbf{Weapon (Primary):} \textit{Ares Predator,
   Ranger Arms}

\textbf{Weapon (Silent):} \textit{Taser, Narcoject
Rifle, Crossbow}


\paragraph{6.  Choose your cyberware}

You may start with one of the following cyber-
ware kits (descriptions of these items are on
page 45):

\textbf{Kit 1 (2 essence):} \textit{Cybereyes with
  low-light/camera, Cyberears with Noise Filter/Recorder}

\textbf{Kit 2 (4 essence):} \textit{Wired Reflexes
  1, active camouflage}


\paragraph{7.  Set your Essence and Edge.}

To determine your starting Essence, subtract the
essence cost of your cyberware (if any) from 6.

You start with 3 Edge.

\paragraph{8.  Choose 2 Contacts}




\paragraph{9.  Establish debts and favors}

Place one of your fellow runners’ names in at
least one of the blanks in the \textbf{Debts \& Favors}
section of your playbook. Each time a name
appears in a debt or favor, it counts as 1 Bond
with that character. The more people you have
Bond with, the better.

\paragraph{10.  Starting Funds}

You start play with 3d6 x 150¥ immediately
available.

\paragraph{11.  Starting Moves}

You know all the Core and Secondary Moves.
You also know the \textbf{Ghosting} move and
one other Covert Ops move.

\end{multicols}

\newpage

\begin{dossier}
\dossierstatbar{COVERT OPS SPEC}
\hspace{.5cm}%
\vrule width 2pt
\hspace{.3cm}%
\begin{dossiermovebar}
\fontsize{9pt}{1em}\selectfont
\setlength{\parskip}{.2cm}

\selectedMove{Ghosting:} when you attempt to avoid detection,
roll+Awareness. On a 10+, your presence is
completely undetected. On a 9-7, you escape
detection, but suspicions are raised and you take
a -1 to your future Ghosting attempts. The penalty
will stack until you achieve 10+ at Ghosting or
leave the secure 

\unselectedMove{ Act of God:} when you attempt to
snipe a target from long range, roll+Combat. On a
10+, choose 2. On a 9-7, choose one:
\begin{moveoptions}
\moveoption{You make the shot without exposing
  your position}

\moveoption{You hit the target precisely where you
wanted to}

\moveoption{You don't expend any ammunition}
\end{moveoptions}

\unselectedMove{Cat Burglar:} while climbing, you
are boosted when Staying Frosty.

\unselectedMove{Plan B:} when you fail a Ghosting move, instead of marking XP you may
roll+Combat. On a 10+, take +2 forward towards
your next Rock \& Roll move. On 7-9, take +1 forward.

\unselectedMove{Standard Architecture:} when you
attempt to navigate within a building,
roll+Craft. On 10+, you are able to find your way
without any trouble. On 7-9, you know the way, but
encounter unexpected trouble on route.

\unselectedMove{Shadow Operator} when you achieve a
10+ at Rock \& Roll under poor lighting
conditions, you may opt to deal no damage to your
opponent but instead silently disable them.

\unselectedMove{Security Bypass} when attempting
to bypass a security lock, roll+Craft. On a 10+,
you successfully disable the lock. On a 7-9, you
disable the lock, but choose one:
\begin{moveoptions}
\moveoption{disabling the lock sets off a remote
  alarm}

\moveoption{in your attempts, you damage the
  device visibly}

\moveoption{it takes a long time to disable the lock}

\end{moveoptions}

\unselectedMove{Sight Unseen} when you
successfully infiltrate and then exit a  building
without being detected, gain +1 hold.

\unselectedMove{One of Many} if you hide in a
crowd, take +1 to your Ghosting move.

\unselectedMove{Magic Bullet} when executing an
Act of God, add the following as a possible result
to select from:
\begin{moveoptions}
\moveoption{In addition to your primary target, you strike
  a second, close-by, target}
\end{moveoptions}

\end{dossiermovebar}%
\end{dossier}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "sixth_world"
%%% End: 
