\invisiblepart{DOSSIER : MAGE}

\section{THE MAGE}
\begin{multicols}{3}
\setlength{\parskip}{.05cm}

\texttt{>>>It’s not easy to study these formulae. Trust me, it’s like
learning a language spoken by creatures with ten mouths,
twelve eyes, and a tonal language based on what the color
nine smells like. If you haven’t got the gift, well...if you’re
lucky, it’ll look like gibberish. If you’re unlucky, it might just
bust your head. But do you know what it’s like to turn invis-
ible, to throw lightning from your hands, or to heal injuries
with a word? To be the artillery when a run goes south hard?
You know what it’s like?}

\texttt{It’s a little like being a god.<<<}

\textbf{The Mage}’s magical talent is focused on the Arcana art
of spellcasting - employing esoteric formulas, incanta-
tions, and the precepts of magical theory to shape
reality itself. If you want an Arcana artillery company,
someone to cloak the entire team in magical invisi-
bility, or someone to provide astral overwatch for the
whole team, look to the mage.


\subsection{CREATING A MAGE}

\paragraph{1.  Choose your Metatype}

You may choose \textbf{Human}, \textbf{Dwarf}, \textbf{Elf}, \textbf{Ork}, or
\textbf{Troll}. Each metatype offers a selection of meta-
type moves. Choose one metatype move from
the options presented.

\paragraph{2.  Choose your look}

\textit{Blank eyes, unnatural eyes, piercing eyes}

\textit{Long hair, bald, wild hair}

\textit{Robes, street clothes, dress clothes}

\textit{Thin body, weak body, muscular body}

\paragraph{3.  Choose your name and street name}

Make up a name and street name or pick a real
name and street name from the lists and name
generators starting in the \textbf{GM Resources} section.

\paragraph{4.  Assign your stats}

You have 5 stats: Awareness, Combat, Stamina,
Craft, and Presence. Important stats for you are
Craft, Awareness, and Stamina.

You have 4 \textbf{Build Points} to distribute among
your stats. To increase a stat by 1 point costs 1
Build Point. You may increase a stat to a maxi-
mum of +2 as a starting character. If you wish,
you may lower 1 stat to -1 in order to have an
additional point to spend.

\paragraph{5.  Choose your Equipment}

Choose from the lists below, or customize your
own gear using the rules in \textbf{Creating Gear} on
page 60.

\textbf{Armor:} \textit{trenchcoat, light armor jacket, armor
charm}

\textbf{Weapon:} \textit{Beretta 101T, Ruger Super War-
hawk, Staff}

\paragraph{6.  Craft your Spells}

Choose 3 of the following 5 spell categories:

\textit{Combat, Detection, Illusion, Health, Manipulation}

You know 2 spells in one of your chosen catego-
ries, 1 in the second category, and 1 in the final
category. Either choose from the lists of spells on
page 40, or create your spells according to the
\textbf{Spellcrafting} rules on page 67.

\paragraph{7.  Set your Essence and Edge.}

You start with 6 Essence and 3 Edge.

\paragraph{8.  Choose 2 Contacts}

Wage Mage, Corporate Exec, Fetishmonger,
Paranormal Animal Expert, Bartender, Street
Cop, Professor of Magical Theory

\paragraph{9.  Establish debts and favors}

Place one of your fellow runners’ names in at
least one of the blanks in the \textbf{Debts \& Favors}
section of your playbook. Each time a name
appears in a debt or favor, it counts as 1 Bond
with that character. The more people you have
Bond with, the better.

\paragraph{10.  Starting Funds}

You start play with 3d6 x 250¥ immediately
available.

\paragraph{11.  Starting Moves}

You know all the Core and Secondary Moves.

You also know the \textbf{Cast a Spell} and \textbf{Counterspell} moves.

\end{multicols}

\newpage


\begin{dossier}
\dossierstatbar{THE MAGE}
\hspace{.5cm}%
\vrule width 2pt
\hspace{.3cm}%
\begin{dossiermovebar}
\fontsize{9pt}{1em}\selectfont
\setlength{\parskip}{.01cm}

\selectedMove{Cast a Spell:} When you cast a spell, choose the spell's force and roll. What stat you add 
depends on the spell type: 
\begin{moveoptions}
\moveoption{ \textbf{Combat:} roll+Combat }

\moveoption{ \textbf{Health:} roll+Stamina }

\moveoption{ \textbf{Detection:} roll+Awareness }

\moveoption{ \textbf{Manipulation:} roll+Craft }

\moveoption{ \textbf{Illusion:} roll+Presence }
\end{moveoptions}

For every 3 points of force, take -1 to the roll. The force can not exceed twice your essence.

On 10+, you cast the spell without trouble. On 7-9, you cast the spell, but (choose 1): 
\begin{moveoptions}

\moveoption{ it causes drain; take the spell's force divided by 2 as stun. If the force is greater than your current essence, the damage is physical. }

\moveoption{ it causes astral feedback; you are glitched for the next spell you cast }

\moveoption{ you must expose yourself to danger or an attack to cast the spell }
\end{moveoptions}

\selectedMove{Counterspell:} to disrupt or end a spell cast by another towards yourself or an ally, roll+Craft. 
On 10+, the spell is dispelled. On 7-9, the disruption was draining; take 2 stun.

\unselectedMove{Center:} when you take a moment to concentrate and restore yourself, hold 2 for future spell casting or counterspelling.

\unselectedMove{Specialist:} choose a spell category.You take +1 when casting spells from that category. 

    \unselectedMove{Astral Trace:} when you observe a magical effect for which you cannot determine the 
      source, roll+Awareness. On a 10+, the GM answers three of the following. On 7-9, two: 
\begin{moveoptions}

      \moveoption{ In what direction does the source of this magic lie? }

      \moveoption{ Approximately how far away is the source? }

      \moveoption{ What is the general nature of the source (metahuman, astral, para-animal)? }

      \moveoption{ How powerful is the source? }
\end{moveoptions}

      \unselectedMove{Imbue Focus:} when you craft a magical focus, permanently reduce your Edge by 1, and roll+Craft. On 10+, 
        the focus is successfully created. On 7-9, the focus is created, but you must spend twice as 
        much Edge to craft it. Imbuing a focus takes 1 day. 

        \unselectedMove{Hermetic Library:} you have permission to access an extensive library of hermetic lore. 
          When you or a teammate uses the Citation Needed move to research magical history or 
          theory, the move is boosted. 

\unselectedMove{Mana Barrier:} to construct a mana barrier, roll+Craft. On 10+ the barrier is formed. On 7-9, the barrier is formed, but you suffer 2 stun as drain. If created, the barrier's force is equal to your roll-6.

\unselectedMove{Quickening:} when sustaining a spell, you may spend Edge equal to the spell's force to create a self-sustaining spell. This eliminates it's sustaining penalty, but ties up the Edge spent until the spell is dismissed or disrupted.

\unselectedMove{Absorption:} when you successfully counterspell, roll+Stamina. On 10+, hold +2 for your next spell casting move. On 7-9, hold +1. 


\begin{comment}
             \unselectedMove{Initiate:} when you hit the books, you may also spend the Prep earned to: 
\begin{moveoptions}

              \moveoption{ reduce a spell’s Essence cost by 1 (this can reduce the cost to 0) }

                \moveoption{ boost a Cast a Spell move }

                \moveoption{ restore 1 essence }
\end{moveoptions}
\end{comment}



\end{dossiermovebar}%
\end{dossier}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "sixth_world"
%%% End: 
