\invisiblepart{DOSSIER : MERCENARY}

\section{THE MERCENARY}
\begin{multicols}{3}
\setlength{\parskip}{.05cm}

\texttt{>>>I’ve fought in a dozen little brush wars - and some big
ones - over the years. I’ve seen a lot of shit go down. Once I
got out, though, I wasn’t good for much except killing peo-
ple and breaking things. Upside: those are pretty marketable
skills in 2050. Seems like everybody in the damn country
wants somebody dead or something destroyed.}

\texttt{So I did my time with a few crews. Some pros. Some...not. I
try to maintain a code, though, and after a while I decided
that freelance work was where it’s at. That was a learning
experience. Some of these supposedly shit-hot runners need
to learn a few essentials, like “don’t set up the ambush so you
shoot your own guys” and what “enfilade” means. Makes me
cringe sometimes.}

\texttt{Still, I’ve got a good team, I set my own hours, and I get to
decide whether melting down a busload of nuns is worth the
pay.<<<}

\textbf{The Mercenary} served in one of the many military
forces found in the Sixth World, doing time in conflicts
large and small, and brought from that solid tactical
abilities and a respectable repertoire of combat tal-
ents. Hardened mentally and physically from years in
service, the merc is highly skilled in combat and has
the added benefit of leadership experience that can
save the team’s bacon when things get hairy.



\subsection{CREATING A MERCENARY}

\paragraph{1.  Choose your Metatype}

You may choose \textbf{Human}, \textbf{Dwarf}, \textbf{Elf}, \textbf{Ork}, or
\textbf{Troll}. Each metatype offers a selection of meta-
type moves. Choose one metatype move from
the options presented.

\paragraph{2.  Choose your look}

\textit{Dead eyes, cold eyes, soft eyes}

\textit{Boonie hat, crew cut, ponytail, fauxhawk}

\textit{Combat fatigues, street clothes, nice suit}

\textit{Scarred skin, tough skin, soft skin}

\paragraph{3.  Choose your name and street name}

Make up a name and street name or pick a real
name and street name from the lists and name
generators starting in the \textbf{GM Resources} section.

\paragraph{4.  Assign your stats}

You have 5 stats: Awareness, Combat, Stamina,
Craft, and Presence. Important stats for you are
Combat, Stamina, and Presence.


You have 4 \textbf{Build Points} to distribute among
your stats. To increase a stat by 1 point costs 1
Build Point. You may increase a stat to a maxi-
mum of +2 as a starting character. If you wish,
you may lower 1 stat to -1 in order to have an
additional point to spend.

\paragraph{5.  Choose your Equipment}

Choose from the lists below, or customize your
own gear using the rules in \textbf{Creating Gear} on
page 60.

\textbf{Armor:} \textit{ballistic vest, armor jacket, combat
armor}

\textbf{Weapon (choose 3):} \textit{Ares Predator, Browning
Max Power, AK-97K, Ingram Smartgun, Colt
M22A2, AK-97, tomahawk, combat knife}


\paragraph{6.  Choose your cyberware}

You may start with one of the following cyber-
ware kits (descriptions of these items are on
page 45):

\textbf{Kit 1 (3 essence):} \textit{level 1 wired reflexes, hand
razors}

\textbf{Kit 2 (3 essence):} \textit{cybereyes with low-light/
vision magnification, active camouflage}


\paragraph{7.  Set your Essence and Edge.}

To determine your starting Essence, subtract the
essence cost of your cyberware (if any) from 6.

You start with 3 Edge.

\paragraph{8.  Choose 2 Contacts}

Former CO, Terrorist Cell Member, Arms Dealer,
Veterans Clinic Doctor, Old War Buddy, Street
Pharmacist, Therapist


\paragraph{9.  Establish debts and favors}

Place one of your fellow runners’ names in at
least one of the blanks in the \textbf{Debts \& Favors}
section of your playbook. Each time a name
appears in a debt or favor, it counts as 1 Bond
with that character. The more people you have
Bond with, the better.

\paragraph{10.  Starting Funds}

You start play with 3d6 x 150¥ immediately
available.

\paragraph{11.  Starting Moves}

You know all the Core and Secondary Moves.
You also know the \textbf{Go Tactical} move and
one other Mercenary move.

\end{multicols}

\newpage

\begin{dossier}
\dossierstatbar{THE MERCENARY}
\hspace{.5cm}%
\vrule width 2pt
\hspace{.3cm}%
\begin{dossiermovebar}
\fontsize{9pt}{1em}\selectfont
\setlength{\parskip}{.2cm}

\selectedMove{Go Tactical:} when you Check the Situation during combat, roll+Combat instead of
+Awareness. On a 10+, instead of asking the GM questions, you may instead choose to Hold
3. On a 7-9, you may choose to Hold 1.
\begin{moveoptions}
\moveoption{ You can then spend that Hold 1-for-1
  to grant a bonus to any ally at any point during
  the combat.}
\end{moveoptions}
\unselectedMove{ Combat Instincts:} Boost your first Rock \& Roll move in a fight.

\unselectedMove{ Leatherneck:} when you take damage, roll+Stamina. On 10+, reduce the damage by 3.
On 7-9, reduce the damage by 1.

\unselectedMove{ CQC Expert:} when you Rock \& Roll using a melee weapon or while unarmed,
deal +1d4 damage.

\unselectedMove{ Veteran:} when you Stay Frosty, you take +1.

\unselectedMove{ Adapt and Overcome:} when you fail a move, instead of marking XP you may
roll+Craft. On 10+, take +2 forward to your next move. On 7-9, take +1 forward.

\unselectedMove{ Contracts Available:} you have contacts with a mercenary force or guild. Roll+Presence.
On 10+, they can pass you a contract worth 10,000¥. On 7-9, they can pass you a contract
worth 5,000¥.

\unselectedMove{ Field Trial:} when you use your military connections to acquire military-only equipment,
roll+Presence. On 10+, you’re able to borrow the equipment for 5 days. On 7-9, you borrow
the equipment, but (choose 1):
\begin{moveoptions}
\moveoption{ There’s an unscheduled inventory inspection before you can return it}

\moveoption{ You need to pony up a sizeable “security deposit”}

\moveoption{You got a hangar queen. The equipment
  requires 1 day of maintenance, or it will fail
  at a most inopportune moment.}
\end{moveoptions}
\unselectedMove{ Inspiring:} when you roll a 10+ when you Stay Frosty, one ally who saw you can take +1
to their next move.

\unselectedMove{ Dodge This:} when you manage to get out of an enemy’s line of sight, roll+Craft. On
10+, you get the drop on that enemy when you reappear. On 7-9, you take +1 forward
against that enemy when you reappear.

\end{dossiermovebar}%
\end{dossier}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "sixth_world"
%%% End: 
